Real-Time Application of Activity Classification from Body-Worn Accelerometers

### 2016-06-06 notes/paper/paper.tex
incremental changes to the paper.

The matched filter is based on the cross correlation of the data $\vec{y} = \{y\}_{k=0}^{N-1}$ with the reference signal $\vec{x} = \{x\}_{k=0}^{M-1}$.
The cross correlation of $\vec{x}$ with $\vec{y}$ is defined as:
%
\begin{equation} \label{cross_correlation_eq}
(\vec{x} \star \vec{y}) = \left \{\sum_{i=0}^{M}(x_{i} y_{(i+k)\%N}) \right \}_{k=0}^{N-M}
\end{equation}
%
which is simply a moving dot product. Here we use $(i+k)\%N$ to represent $i+k$ modulo $N$.
We can then normalize \eqref{cross_correlation_eq} by the following:
%
\begin{equation} \label{norm_cross_correlation_eq}
\widehat{(\vec{x} \star \vec{y})}_k = \frac{(\vec{x} \star \vec{y})_k}{||\vec{x}|| \ || \{y_p\}_{p=k}^{M+k} || }, \quad k = 0,1,...,N-M-1
\end{equation}
%
where $|| \cdot ||$ is the usual $L_2$ norm. \eqref{norm_cross_correlation_eq} is now bound by $[-1,1]$ and has any bias toward high energy removed.
We improve our computational efficiency by applying the convolution theorem to \eqref{cross_correlation_eq} and replacing it with:
%
\begin{equation} \label{conv_theorem}
(\vec{x} \star \vec{y}) = FFT^{-1}(FFT(\vec{x}') FFT(\vec{y})^*)
\end{equation}
%
Where $\vec{x}'$ is $\vec{x}$ that has been zero padded to the length of $\vec{y}$ with the added restriction that the length of $\vec{x}$ is no more than the length of $\vec{y}$ to prevent corruption from circular indexing.
We are most interested where our reference best matches our data.
The resulting max correlation yields our matched-filter output:
%
\begin{equation} \label{matched_filter_eq}
MF(\vec{x},\vec{y}) := \underset{k \in [0, M-N]}{max} \left \{\widehat{(\vec{x} \star \vec{y})}_k \right \}
\end{equation}
%
\section{Dimensionality Reduction}
We manage to reduce our computational resources and remove our dependence on sensor orientation at the same time through a process of dimensionality reduction.
We assume that over a short period of time, a user\textquotesingle s limb movement is constrained mostly to a two-dimensional plane.
By identifying the plane of motion, we then project the acceleration data onto this plane and re-define our $x$ and $y$ axis accordingly.
By this assumption, activities that are mostly confined to two dimensions will improve our signal identification.

If we let $\{\vec{a}_i\}_{i=0}^{N}$ represent our demeaned acceleration data over some time window $T$ in $\mathbb{R}^3$ then the covariance matrix of our acceleration data is represented by the real-symmetric $3x3$ matrix $Q = \vec{a} \vec{a}^T$.
The resulting eigen vectors of this matrix are orthogonal and point in the directions where the data varies most [cite from some text book here].
By projecting our data on the plain defined by the two most dominant eigen vectors, we effectively reduce our representation of our data to two dimensions.
%
\section{Training the Module}
We are able to identify an individual\textquotesingle s activity by matching the signal to a reference template.
For our application, we develop a reference signature for our matched filter directly from the person\textquotesingle s motion signature.
We do this by having the individual perform the specific activity over a specified amount of time and select the sub-interval of time that we find best represents the user's motion signature.
For a given activity, we attempt to find the representative periodic signal $s$ of our individual’s activity to be our template for our matched-filter.

>>>>

The matched filter is based on the cross correlation of the data $\vec{y} = \{y\}_{k=0}^{N-1}$ with the reference signal $\vec{x} = \{x\}_{k=0}^{M-1}$.
The cross correlation of $\vec{x}$ with $\vec{y}$ is defined as:
%
\begin{equation} \label{cross_correlation_eq}
(\vec{x} \star \vec{y}) = \left \{\sum_{i=0}^{M}(x_{i} y_{i+k}) \right \}_{k=0}^{N-M-1}
\end{equation}
%
which is simply a moving dot product.
We can then normalize \eqref{cross_correlation_eq} by the following:
%
\begin{equation} \label{norm_cross_correlation_eq}
\widehat{(\vec{x} \star \vec{y})}_k = \frac{(\vec{x} \star \vec{y})_k}{||\vec{x}|| \ || \{y_p\}_{p=k}^{M+k} || }, \quad k = 0,1,...,N-M-1
\end{equation}
%
where $|| \cdot ||$ is the usual $L_2$ norm. \eqref{norm_cross_correlation_eq} is now bound by $[-1,1]$ and has any bias toward high energy removed.
We improve our computational efficiency by applying the convolution theorem to \eqref{cross_correlation_eq} and replacing it with:
%
\begin{equation} \label{conv_theorem}
(\vec{x} \star \vec{y}) = FFT^{-1}(FFT(\vec{x}') FFT(\vec{y})^*)
\end{equation}
%
Where $\vec{x}'$ is $\vec{x}$ that has been zero padded to the length of $\vec{y}$ with the added restriction that the length of $\vec{x}$ is no more than the length of $\vec{y}$ to prevent corruption from circular indexing.
We are most interested where our reference best matches our data.
The resulting max correlation yields our matched-filter output:
%
\begin{equation} \label{matched_filter_eq}
MF(\vec{x},\vec{y}) := \underset{k \in [0, M-N]}{max} \left \{\widehat{(\vec{x} \star \vec{y})}_k \right \}
\end{equation}
%
\section{Dimensionality Reduction}
We manage to reduce our computational resources and remove our dependence on sensor orientation at the same time through a process of dimensionality reduction.
We assume that over a short period of time, a user\textquotesingle s limb movement is constrained mostly to a two-dimensional plane.
By identifying the plane of motion, we then project the acceleration data onto this plane and re-define our $x$ and $y$ axis accordingly.
By this assumption, activities that are mostly confined to two dimensions will improve our signal identification.

If we let $\{\vec{a}_i\}_{i=0}^{N}$ represent our demeaned acceleration data over some time window $T$ in $\mathbb{R}^3$ then the covariance matrix of our acceleration data is represented by the real-symmetric $3x3$ matrix $Q = \vec{a} \vec{a}^T$.
The resulting eigen vectors of this matrix are orthogonal and point in the directions where the data varies most [cite from some textbook here].
By projecting our data on the plain defined by the two most dominant eigen vectors, we effectively reduce our representation of our data to two dimensions.
%
\section{Training the Module}
We are able to identify an individual\textquotesingle s activity by matching the signal to a reference template.
For our application, we develop a reference signature for our matched filter directly from the person\textquotesingle s motion signature.
We do this by having the individual perform the specific activity over a specified amount of time and select the sub-interval of time that we find best represents the user's motion signature.
For a given activity, we attempt to find the representative periodic signal $s$ of our individual’s activity to be our template for our matched-filter.
